---
title: "Dutch Environmental Permit Application Process: CoSeLoG"
author: "bdanalytics"
#date: "December 9, 2014"
#output: pdf_document
output: 
    pdf_document:
        toc: true
        number_sections: true
        highlight: zenburn
---
#### Date: `r format(Sys.time(), "(%a) %b %d, %Y")`    

```{r, echo=FALSE}
print("a blank line")   
```
Data: Originates from the CoSeLoG project executed under NWO project number 638.001.211. Within the CoSeLoG project the (dis)similarities between several processes of different municipalities in the Netherlands has been investigated. This event log contains the records of the execution of the receiving phase of the building permit application process in an anonymous municipality.

Source: http://data.3tu.nl/repository/uuid:a07386a5-7be3-4367-9535-70bc9e77dbe6

Time period: 2010-10-02 to 2012-01-23

### Synopsis:

#### Potential next steps include:

```{r set_global_options, echo=FALSE}
rm(list=ls())
set.seed(12345)
#source("~/Dropbox/datascience/R/mydsutils.R")
#source("~/Dropbox/datascience/R/myplot.R")
# Gather all package requirements here
#suppressPackageStartupMessages(require())

#require(sos); findFn("pinv", maxPages=2, sortby="MaxScore")
```

```{r set_global_options_wd, echo=FALSE}
setwd("~/Documents/Work/Courses/Coursera/process-mining/Projects/PM_Assignment")
```

### Step 01: import data
```{r import_data, cache=TRUE}


```